On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2020-08-13 paper/cav_determinisim_main.tex
changed entries wrt accuracy

% GC Text
\todo[inline]{GC Edit: Determinism is a key prerequisite for simulation during AV development and testing. A deterministic simulation environment guarantees that tests are repeatable, or more formally, are \textit{precise}. The \textit{precision} of the process is the ability of the simulation to repeat the same execution and find no, or a \textit{tolerable}, difference in the outcome. Therefore \textit{tolerance} is the acceptable degree of variability between execution outputs. When the simulation output is within tolerance, coverage results are stable and, when a test fails, debugging can rely on the test producing the same trace and outcome when repeated. This ensures that software bugs can be found and fixed efficiently, and that simulation results are trustworthy. }
%
%Any software defects that are detected but not repeatable at a later time or by another party does not allow for suitable resolution. Furthermore, defects not found on the verification testing system may arise on a deployed system with a different hardware architecture resulting in untested and potentially unsafe behaviour. 
%When considering the development of autonomous vehicles, untested code could lead to dangerous behaviours not being identified and fatal road accidents may occur.
%
If the simulation is not deterministic, however, variance in actor positions, for instance, may lead to assessment errors, making it difficult to understand and remove bugs. In the worst case, bugs that could have been identified in simulation remain undetected, resulting in false confidence in the safety of the AV's control software.

@@

Considering the objectives for gaming and comparing them to these for AV development and testing, there are fundamental differences. 
%
Providing game players with a responsive real-time experience is often achieved at the cost of simulation accuracy.
%
In contrast, simulation accuracy is essential in AV development and testing, especially for perception stack testing, but also for visual inspection of accidents or near misses. If necessary, it is acceptable to achieve the required level of accuracy at the cost of real-time performance. 
%
For example, for perception stack testing the sensors need to get input that is as close as possible to what the real input would be, i.e.\ with no or minimal extrapolation or lag. This  may only be realisable by slowing down the rendering to enable more extensive physics calculations. \todo{KIE: ... by slowing down the simulation to enable more extensive physics calculations?}

>>>>

% GC Text
\todo[inline]{GC Edit: Determinism is a key prerequisite for simulation during AV development and testing. A deterministic simulation environment guarantees that tests are repeatable, or more formally, are \textit{precise}. This is not to be confused with \textit{accuracy} that describes the extent to which the simulation complies to a known standard, which could be considered a level of realism that faithfully describes the real world. The \textit{precision} of the process is the ability of the simulation to repeat the same execution and find no, or a \textit{tolerable}, difference in the outcome. Therefore \textit{tolerance} is the acceptable degree of variability between execution outputs. When the simulation output is within tolerance, coverage results are stable and, when a test fails, debugging can rely on the test producing the same trace and outcome when repeated. This ensures that software bugs can be found and fixed efficiently, and that simulation results are trustworthy. }
%
%Any software defects that are detected but not repeatable at a later time or by another party does not allow for suitable resolution. Furthermore, defects not found on the verification testing system may arise on a deployed system with a different hardware architecture resulting in untested and potentially unsafe behaviour. 
%When considering the development of autonomous vehicles, untested code could lead to dangerous behaviours not being identified and fatal road accidents may occur.
%
If the simulation is not deterministic, however, variance in actor positions, for instance, may lead to assessment errors, making it difficult to understand and remove bugs. In the worst case, bugs that could have been identified in simulation remain undetected, resulting in false confidence in the safety of the AV's control software.

@@

Considering the objectives for gaming and comparing them to these for AV development and testing, there are fundamental differences. Providing game players with a responsive real-time experience is often achieved at the cost of simulation accuracy. In contrast, simulation accuracy is essential in AV development and testing, especially for perception stack testing, but also for visual inspection of accidents or near misses. If necessary, it is acceptable to achieve the required level of accuracy at the cost of real-time performance. For example, for perception stack testing the sensors need to get input that is as close as possible to what the real input would be, i.e.\ with no or minimal extrapolation or lag. This  may only be realisable by slowing down the rendering to enable more extensive physics calculations.

\todo[inline]{GC Edit: Considering the objectives for gaming and comparing them to these for AV development and testing, there are fundamental differences. Providing game players with a responsive real-time experience is often achieved at the cost of simulation accuracy and precision. The gamer neither wishes a faithful representation of reality, i.e. can be low accuracy, nor do they require for repeated actions to result in the same outcome to particular tolerance, i.e. can be low precision. In contrast, the precision required for AV development and testing is much higher, especially for perception stack testing, but also for visual inspection of accidents or near misses. If necessary, it is acceptable to achieve the required level of tolerance on the precision at the cost of real-time performance. For example, for perception stack testing the sensors need to get input that is as close as possible to what the real input would be, i.e.\ with no or minimal extrapolation or lag. This  may only be realisable by slowing down the rendering to enable more extensive physics calculations.}

\todo{KIE: ... by slowing down the simulation to enable more extensive physics calculations?}
